A Classical Density-Functional Theory for Describing Water Interfaces

### 2013-08-13 papers/water-saft/paper.tex

An important aspects of water
is its ability to form hydrogen bonds.  Each water molecule contains
two hydrogen bond donor sites and two acceptor sites.

@@

@@

SAFT is based on Wertheim's first-order thermodynamic perturbation
theory (TPT1)\cite{wertheim1984fluidsI, wertheim1984fluidsII,
  wertheim1986fluidsIII, wertheim1986fluidsIV}, which allows it to
account for strong associative interactions between
molecules. Wertheim's thermodynamic perturbation theory uses a
hard-sphere reference fluid where each sphere has a number of
association sites on the surface. The association sites have an
effective range and a small energy contribution when a site is within
range of another hard-sphere's site. The free energy due to this
association depends on the radial distribution function
$g_\sigma^\text{HS}(\rr)$. Our previous water functional used Yu and
Wu's radial distribution function
\cite{yu2002fmt-dft-inhomogeneous-associating}, which was found to
agree less with hard-sphere Monte-Carlo simulation than a distribution
function developed by us in a recent paper \cite{schulte2012using}. In
our paper, we developed an approximation for correlation at
contact to describe the hard-sphere fluid.

>>>>

@@

SAFT is based on Wertheim's first-order thermodynamic perturbation
theory (TPT1)\cite{wertheim1984fluidsI, wertheim1984fluidsII,
  wertheim1986fluidsIII, wertheim1986fluidsIV}, which models
\fixme{fluids} as hard-spheres with strong associative interactions at
sites on the surfaces of the spheres. This is ideal for water, since
its four hydrogen bond sites can be represented by these association
sites. The association sites have an effective range and a small
energy contribution when a site is within range of another
hard-sphere's site. The free energy due to this association depends on
the radial distribution function $g_\sigma^\text{HS}(\rr)$. Our
previous water functional used Yu and Wu's radial distribution
function \cite{yu2002fmt-dft-inhomogeneous-associating}, which was
found to agree less with hard-sphere Monte-Carlo simulation than a
distribution function developed by us in a recent paper
\cite{schulte2012using}. In our paper, we developed an approximation
for correlation at contact to describe the hard-sphere fluid.

@@
